Generative Adversarial Networks

### 2017-11-12 cs6735/project/draft.tex
init background section

>>>>

When compared to other generative models, especially deep generative models, GANs possess several advantages... quicker? no Markov chains?

\begin{figure}
\centering
\includegraphics[scale=0.65]{img2img}
\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}. This approach makes use of conditional generative adversarial networks to map image domains.}
\label{fig:Image to Image Examples}
\end{figure}

\section{Background}
